Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-03 writing/DraftExposurePaper/DraftExposurePaper.Rmd
edit text

# Create a new dataset for precip with lag -5 to 3 for fips 12086 only

@@

all_dates <- unique(check_dates$date)
all_fips <- unique(check_dates$fips) # has Miami as "12086", and is still in check_dates here

>>>>

# Create a new dataset for precip with lag -2 to 3 for fips 12086 only

@@

all_dates <- unique(check_dates$date)
all_fips <- unique(check_dates$fips)
